Technical Report

### 2018-06-22 fully-abstract-comp/technical-report.tex
Remove obsolete comment.
Discharge a technical proof.
Standardize naming a bit.

\section{Full Abstraction}
\label{sec:full-abstraction}
\lau{TODOs from last day in Leuven}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}

@@

\section{Lemmas}
\begin{lemma}
  \label{lem:unique-h-sigma}
  if $\iota,iota' \in \dom(\pwheap)$ and $\pwheap(\iota) = (\pure,\_,H_\sigma)$
  and $\pwheap(\iota') = (\pure,\_,H_\sigma')$ and $\sigma \in \dom(H_\sigma)$
  and $\sigma \in \dom(H_\sigma')$ and $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$,
  then
  \[
    H_\sigma = H_\sigma' \text{ and } \iota = \iota'
  \]
\end{lemma}
\begin{proof}
  \lau{TODO}
\end{proof}

>>>>

\section{Full Abstraction}
\label{sec:full-abstraction}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}

@@

\section{Lemmas}
\begin{lemma}
  \label{lem:unique-h-sigma}
  If $r,r' \in \dom(\pwheap)$ and $\pwheap(r) = (\pure,\_,H_\sigma)$
  and $\pwheap(r') = (\pure,\_,H_\sigma')$ and $\sigma \in \dom(H_\sigma)$
  and $\sigma \in \dom(H_\sigma')$ and $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$,
  then
  \[
    H_\sigma = H_\sigma' \text{ and } r = r'
  \]
\end{lemma}
\begin{proof}
  This follows easily by definition of $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$ and $\lrheap$.
\end{proof}
